Summary Tables

### 2019-12-10 summary_tables.Rmd
Add 9 cities, and then respective dist_cat tables

```{r load_objects = "asis"}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore')
# cities <- c('sao_paulo')

@@

@@

for(city in cities){
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% summarise(uid <- n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('baseline', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]

>>>>

```{r load_objects = "asis"}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore', 'santiago', 'belo_horizonte', 'buenos_aires', 'mexico_city','bogota')

# cities <- c('sao_paulo')

@@

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 92.4|29.7|0.3 |
| bicycle | 1.5|10.5|2.5 |
| car | 5.4|42.3|27.4 |
| motorcycle | 0.0|0.6|0.7 |
| bus | 0.0|3.1|36.0 |

|belo_horizonte|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 91.7|36.0|0.6 |
| bicycle | 0.4|3.6|1.0 |
| car | 7.2|39.9|38.9 |
| motorcycle | 0.2|6.6|7.3 |
| bus | 0.0|0.9|39.4 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 95.9|32.9|0.2 |
| bicycle | 3.0|10.1|1.5 |
| car | 0.5|24.1|25.4 |
| motorcycle | 0.0|2.2|1.7 |
| bus | 0.6|27.4|49.9 |

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 95.1|38.1|0.3 |
| bicycle | 0.8|7.7|1.3 |
| car | 2.3|23.9|28.7 |
| motorcycle | 0.0|3.3|1.9 |
| bus | 0.3|19.0|48.3 |

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 94.9|54.5|4.2 |
| bicycle | 2.1|14.3|6.2 |
| car | 1.1|10.3|18.9 |
| motorcycle | 0.0|0.0|0.1 |
| bus | 1.4|17.6|65.7 |

@@

for(city in cities){
  print(city)
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% summarise(uid <- n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('baseline', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
